### 2018-08-17 Sections/costs_and_attributes_in_quantum_networks.tex
Dephasing dist metric

>>>>

A dephasing channel can be easily converted to a distance metric as follows. First we reparameterise the dephasing channel into,
\begin{align}
\mathcal{E}(\hat\rho) &= p\hat\rho + (1-p)\hat{Z}\hat\rho\hat{Z}\nonumber\\
&= (2p-1)\hat\rho + (1-p)(\hat{Z}\hat\rho\hat{Z} + \hat\rho).	
\end{align}
Now \mbox{$2p-1$} is the probability that the state is not dephased and \mbox{$1-p$} is the probability that the state is replaced with the completely dephased state. Therefore the probability of multiple applications of the channel not dephasing the state scales multiplicitavely as,
\begin{align}
p_\mathrm{no\, error} = \prod_{i}(2p_i-1),
\end{align}
which is additive in a logarithmic scale as before,
\begin{align}
\log(p_\mathrm{no\, error}) = \sum_i \log(2p_i-1),
\end{align}
which acts as a distance metric. This approach can similarly be applied to other Pauli channels.
